TCPTokens: Introducing Currency into Datacenter Congestion Control

### 2017-12-09 Documents/Report/Iroko_Report.tex
Update report structure.

%\input{intro}
%
%\input{relatedworks}
%\input{design}
% %\input{motivation}
%\input{implementation}
%\input{eval}
%\input{timeline}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction / Background}
\label{sec:intro}

Initially, research in network congestion was dominated by the assumption of a decentralized, autonomous network - end-hosts only have control over the amount of traffic they send, and are unaware of the intentions or traffic rates of their peers. Similarly, switches and routers are unaware of global traffic patterns and only forward based on their local notion of optimality.

In line with these assumptions, TCP was designed to optimize traffic globally on a simple fairness principle: nodes react to packet loss and assume that others will behave accordingly. An equilibrium is reached when all end-hosts achieve a traffic rate that, in sum, conforms to the maximum available bandwidth of the most congested link.
TCP works well  in scenarios where many different distrustful participants compete for limited bandwidth. Still, TCP is a \textit{reactive protocol}; the fact that packet loss and latency increases occur in the network already indicates a problem. Packet loss is primarily due to overflowing queues in forwarding elements or mismatched hardware capabilities, implying that traffic has not been optimally distributed. Ideally, a network should always be "zero-queue", i.e., latency will merely be induced by propagation, and not queuing delay.

Queueing has commonly not been a dominating issue in wide-area and enterprise networks, as traffic is sufficiently distributed and diverse, with only few "hot" target hosts.~\cite{hedera, microte} Traffic optimization is a substantial challenge; network operators have no control over the individual network elements nor its participants. Under these conditions, TCP and its extensions can be considered a best-effort solution to globally maximize utilization.

Developments in the past decade have changed the general networking environment. Datacenters have emerged as an exciting new research frontier, posing novel design challenges and opportunities. Driven by minimization of costs and maximization of compute power, data centers must  run at maximum utilization to achieve an optimal compute/cost ratio. Inefficient routing can quickly lead to bufferbloat~\cite{bufferbloat} and the eventual collapse of a high-load network, requiring more sophisticated approaches to solve congestion control.

On the other hand, operators now have the ability to freely control and adapt their network architecture, leading to highly customized systems and fine-grained optimization. In such an environment, Software-Defined Networking (SDN) has emerged as a new networking paradigm.~\cite{sdn_road}

Moving away from the principle of distributed communication and routing, SDN introduces the notion of "centralized management". A single controller with global knowledge is able to automatically modify and adapt the forwarding tables of all switches in the network, while notifying end hosts of changes in the network.
These two new trends in system design; full architectural control and centralized management, facilitated new opportunities in the space of TCP congestion research. Traffic can now be managed in a  \textit{centralized} fashion based on \textit{global knowledge} of the entire topology and traffic patterns.

A new line of centralized schedulers has emerged that can achieve close to optimal bandwidth utilization.~\cite{hedera, fastpass, microte, b4, dionysus}
However, these schedulers are still  \textit{reactive}  in nature. The central controller responds to changes in the network or requests by applications, which may cost valuable round-trip latency. Often, short-term flows or bursts are unaccounted for, which causes undesirable packet loss and back-propagating congestion.

The idea of admission control and service guarantees in networks is not new.~\cite{access_limit, access_limit2}. However, such designs traditionally aim to assure quality and bandwidth guarantees in a contentious, decentralized, and untrusted environments such as the internet. In a datacenter, these conditions do not apply. End-hosts are generally considered reliable and restricted in behavior, which allows for great simplification of enforcement and prioritization policies.

A desirable solution is a global, centralized arbiter which is able to predict and fairly distribute flows in the network before bursts or congestion even occur. By treating the network's compute and forwarding power as a single finite resource, a controller acts akin to a OS scheduler distributing CPU time slices to processes. This design approach follows SDN's aspiration of introducing operating systems abstractions to the networking domain space.

In this project, we plan to explore the possibilities of a centralized, proactive flow scheduler. We ask ourselves the following research questions:
\begin{enumerate}
    \item What are the requirements for such a centralized, predictive scheduler to succeed?
    \item Is it possible to preemptively regulate a network by analyzing global traffic patterns?
    \item What latency, packet loss and utilization are we able to achieve?
\end{enumerate}

In the scope of this course, we attempt to answer these questions and design a simple predictive scheduler in Mininet. If successful, we will benchmark our results and evaluate the level of utilization compared to contemporary scheduling systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design / Proposed Approach}
\label{sec:design}

\subsection{Overview and Goals}
In our initial simple system, "Iroko", a centralized controller regulates all node traffic by rate-limiting end-hosts. We have opted for a centralized manager in favor of a distributed protocol to leverage the advantages of a global network view.~\footnote{For now, we do not expect our design to scale up to thousands of switches. Iroko is intended for small to mid-tier size data centers, which may benefit from a simplistic, centralized scheduling model.}
By polling each switch individually for port and utilization statistics we are able to infer a global traffic matrix, which we can amalgamate with static routing and topology information.

Iroko guarantees minimal congestion and low average access latency. Reducing network-global packet loss and jitter is the priority and objective function of the arbiter, which will enforce these goals by restricting host bandwidth. In an ideal Iroko system, packet-loss will only rarely, if ever, occur. In respect to the free lunch theorem we aim to trade off maximum bandwidth utilization for optimal system stability and reliable latency.

It is important to note that routing decisions are not in the current scope of Iroko. While it may certainly beneficial to include dynamic and adaptive routing decisions in a predictive scheduler, we do not include these features in the current system due to time and complexity limitations. Iroko operates on static flow routes defined and generated by ECMP. It is assumed that these routes will not vary substantially and that the computed ECMP forwarding hash is consistent.

\subsection{Controlling traffic flow}
Rate-limiting is performed on the granularity of the IP protocol, allowing us to restrict traffic to specific hot regions and to package flows into groups.
End-hosts are guaranteed a limited amount of bandwidth which they may send to each destination address. The traffic window size for any flow is calculated based on the host's current traffic availability. Total bandwidth of a group of flows may never exceed the imposed bandwidth limitation, but nodes are free to distribute the allocated resources on singular subflows.

The central arbiter enforces these bandwidth and access limitations by assigning "tokens" to nodes. These tokens are plain information packets specifying the affected destination address flow, its bandwidth guarantee, and the expiration time. Tokens act as the rate-limiter of the system and form a queue each end-host will cycle through.

When a node opens a flow, it will look up the current bandwidth restriction for the destination IP in its token database and calculate the maximum congestion window possible for the particular TCP connection. In our simple design, flows are always assigned a fair fraction.

Once a token has expired for a particular flow-group, the restrictions of the next token in the queue will be applied. This mechanism is the underlying basis for a predictive access control algorithm and does not require any application level modification. On end-hosts, only the transport layer services will have to be modified.

\subsection{Adapting traffic flow}

Initially, the controller will compute optimal route configuration based on the topology and link bandwidth using a simple heuristic bin-packing approach. End-hosts will be initialized with a fixed low-to-medium bandwidth guarantee that will be adjusted over time. This bandwidth guarantee will be below the host's proportional bi-section bandwidth that would be used to reach any other host. That is, if every end host transfers using the full bandwidth initially allocated to it,  there would be no dropped packets due to congestion.

Of course, this would vastly underutilize network resources, thus the controller will dynamically adjust these allocations to ensure that hosts that require the bandwidth are allocated it, while host that are not currently utilizing all their allocated bandwidth have their allocated bandwidth reduced. To avoid starving hosts, some small amount of bandwidth must always be allocated to a given host even if it not utilizing network resources. Thus, the network, by design, will never reach 100\% utilization.

Conversely however one should rarely see dropped packets due to network congestion. Furthermore, the controller must be able to react quickly to changing bandwidth needs for hosts. Ideally, using a predictive method.

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Topology3}
\caption{Simple sketch of the Iroko architecture. A central scheduler maintains a consistent view of the current network activity and computes the optimal end-host bandwidth distribution. Bandwidth is enforced at end-hosts on a per-IP basis.}
\label{fig:Topology3}
\end{figure}

\subsection{Statistical System}
One potential implementation for our arbiter is to use reinforcement learning. In reinforcement learning, an agent (in our case the arbiter) performs actions in the environment and receives a reward signal from the environment to adjust its decisions in the next epoch ~\cite{Sutton:1998:IRL:551283}. The reward is generally used to represent the goal the agent is trying to achieve. The agent can freely choose whatever actions are necessary to achieve this goal ~\cite{Sutton:1998:IRL:551283}.

The environment in this case is defined as the statistics collected from each switch. This decision is based on the fact that this data is easy to collect and provides a current snapshot of the performance of the network. We wish to optimize over the packet loss, and define the reward to be good if packet loss is decreasing (+1 reward); bad if it is increasing ( -1 reward); and acceptable if packet loss remains the same within a threshold (0 reward). Using this representation, we take full advantage of all the information provided in our data center; This representation is replicable and can be applied beyond the scope of this project.

Given the data center assumption, the number of end-hosts is known in the topology. We can define our arbiter's actions as a discretized representation among an n-dimensional vector where each cell is one of three values: increase decrease, or maintain the allocated bandwidth. This representation offers sufficient complexity. There are $3^n$ possible actions to perform and to achieve optimal results the agent must explore the environment extensively, precluding a significantly larger action space.

A potential improvement to our representation is a hierarchical learning agent. In this case, our arbiter would manage agents for each host and these sub-agents would manage their respective host whether to increase, decrease, or maintain bandwidth for their particular host. This problem can be referred to as hierarchical reinforcement learning~\cite{Borga1993}, but may prove to be beyond the scope of our current proposed solution, although has the added benefit of solving a set of sub-problems to address the global problem of packet loss and simplifies the representation spaces in the sub-problems.

Thus we frame our problem as one which can now be solved using techniques in reinforcement learning. A classic algorithm to consider is the use of SARSA~\cite{Sutton:1998:IRL:551283}, which is an online temporal difference algorithm used in classical reinforcement learning problems. One advantage of SARSA is its online nature~\cite{Sutton:1998:IRL:551283} which promotes more conservative decisions. Given full representation of our environment and actions, we can store information in an artificial neural network which is another popular choice in reinforcement learning literature. This model would store the reward signal information that is used to make future action choices, and is a theoretically proven function approximator which has made intractable environmental representations manageable~\cite{Sutton:1998:IRL:551283}.

%Using this model, we hope to achieve near 0% packet loss and provide a solution that gets somebody fired at google for not having tried it first.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
\label{sec:implementation}
We intend to emulate our system in Mininet~\cite{mininet} to observe traffic patterns and infer a suitable token algorithm. Mininet has proven itself to be a viable tool to model new congestion control algorithms~\cite{mininet_learning}, and will help us prototype our concept efficiently. We will build a custom SDN controller that interacts with traditional OpenFlow software switches as well as end-hosts. End-hosts will run a custom real-world traffic generation script which adjusts based on information packets sent by the controller.
If time permits, we may expand our implementation to MaxiNet, which can emulate large-scale network stress tests on multiple physical hosts.

We initially considered a second implementation alternative in C/C++ based on the FastPass~\cite{fastpass} source code. This would provide us with a fully deployable system which we could fork our implementation from. A major advantage of this approach is the ability to test scenarios and traffic algorithms using real software code.
However, several concerns made us favour a Mininet emulation instead.
Firstly, FastPass relies on DPDK integration, which requires actual hardware interfaces. The central arbiter in the FastPass design would need to run on a dedicated machine, which increases prototyping and development complexity substantially.

Secondly, the FastPass code is highly specialized and optimized research code with only little available documentation. Modifying and evolving the source code will require thorough understanding of kernel and networking development, a significant time-sink. For a class project, these may be major initial hurdles, taking away from the research aspect of the design concept.
Consequently, we have decided to pursue an approach which allows us to quickly develop an understanding of the problem without being obstructed by engineering work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
\label{sec:evaluation}

In the absence of a commercial data center, the implementation of our network design is going to be done on top of mininet with simulated FatTree topologies of varying size. We stress test with iPerf and simulate data center traffic using tcpreplay and packet traces provided by~\cite{traffic} .

To evaluate the general effectiveness of our system, we plan to measure against existing centralized as well as decentralized solutions.
The centralized design will be based on Hedera~\cite{hedera}, a common and influential datacenter scheduler. The decentralized congestion control mechanism will be DCTCP~\cite{dctcp}, a state-of-the-art TCP congestion algorithm.

Since we are primarily concerned about reducing the latency and packet drops while keeping utilisation at maximum, the measurements to get a good insight into how well the design can perform are as follows:
\begin{enumerate}

\item Latency: We are aiming for a low latency network which means that 99th percentile latency in the network across all flows should as low as possible. Latency should be measured when all hosts are sending packets at the maximum limit and also with random traffic patterns. There should be low latency even during sudden bursts as the transmission rate is limited by a base value.

\item Packet drop rate: Ideally this metric will approach zero, as the objective of Iroko is to minimize packet loss.

\item Fairness: Fairness can be tested by introducing a new host to a completely saturated network and increasing the transmission rate to see if all the hosts gets fair share of the total bandwidth. We are assuming all flows should be at equal priority. Differential priority is out of scope.

\item Responsiveness: This metric depends on the predictive power and efficiency of Iroko. It may be interesting to analyze the response time of the central scheduler compared to decentralized DCTCP and TCP. In addition, it is valuable to identify at what data center and flow size the central computing node of the network may become a bottleneck.

\item Network utilization: We will measure the used bandwidth and the total load on the hosts. These metrics can be measured by varying the load from each host. Load to utilization ratio should be 1 until the saturation point and after that utilization should stay stable at the maximum bisection bandwidth.
It is also important to check that there is no starvation happening in any host. This can be measured by simulating random traffic patterns and plotting residual bandwidth and excess load. We expect overall utilization to be lower compared to Hedera and DCTCP. Although Iroko will maximize goodput, we do not measure it on grounds of simplicity.

\end{enumerate}

As baseline we will also compare to the default TCP congestion algorithm to estimate how our scheduler fares against the default case. As our initial simple design is very constrained in its ability to route and control traffic we expect to achieve less overall optimality against DCTCP and Hedera, but still gain a substantial advantage over common TCP.

\section{Timeline}
\label{sec:timeline}
\begin{itemize}
    \item \underline{October 15th:} Finalize draft.
    \item \underline{ October 22nd:} Iterate over literature and thoroughly analyze related work. Set up an initial prototyping environment in Mininet on which each team member can work on.
    \item \underline{October 30th:} Finalize the initial simple design and explore naive congestion modelling in Mininet. Integrate existing Mininet emulations of Hedera and DCTCP.
    \item \underline{November 12th:} Develop initial naive Iroko prototype involving controller and end-host design.
    \item \underline{November 19th:} Develop intelligent centralized congestion control heuristic.
    \item \underline{November 26th:} Run evaluations and microbenchmarks.
    \item \underline{December 3rd:} Iterate and improve the scheduler, explore topology and bandwidth constraints. Test at scale.
    \item \underline{December 10th:} Write report and prepare presentation.
\end{itemize}

>>>>

\input{intro}
%\input{relatedwork}
\input{design}
% %\input{motivation}
\input{implementation}
\input{eval}

### 2017-12-09 Documents/Report/design.tex
Update report structure.

\subsection{Simple System}
In our initial simple TCPToken design, a centralized controller regulates all node traffic by provisioning end-hosts with tokens.
These tokens act as the "currency" of the system. The total amount is fixed to some factor of the aggregate bandwidth available in the network, and the traffic window size of sending end hosts is calculated based on the host's current token availability. If a node or switch is overburdened, it may notify the scheduler, which will adjust the traffic window of responsible sending nodes remotely. Management and control operations including token distribution and updates are priority-queued to guarantee a fast and low-latency response. If an end-host requires more bandwidth, it can also notify the controller, which may comply based on priority and availability.
Initially, the controller will compute optimal route configuration based on the topology and link bandwidth using a simple heuristic bin-packing approach. End-hosts will be initialized with a fixed low-to-medium bandwidth guarantee that will be adjusted over time.

\subsection{Advanced System}
The aforementioned system is intended only as a proof of concept. It is still a  synchronous and reactive approach, dependent on notifications and requests by overburdened switches and underprovisioned hosts. 
Ideally, all management in the TCPToken system should be asynchronous and preemptive. 
\subsubsection{ Paying for traffic}
In a complete design, tokens will be used as a transport pass instead of simply acting as traffic shaping parameters. On a per-flow basis, nodes will be able to attach tokens to traffic as a form of payment. Enforcement is performed on the switch level, any flow that is not “paid” by a token will be dropped. Nodes may be handed different types of tokens to serve load-balancing and traffic shaping purposes. Applications operating on traditionally short-lived flows and bursts may sign their traffic with a different token type than long-lived permanent processes. Switches will forward traffic and balance flows accordingly with only minor interference from the central controller.

\subsubsection{Predicting traffic}
ML-based scheduling is an emerging research field, also known as Knowledge-Defined Networking. Datacenter traffic follows patterns, which can be predicted using statistical methods.
Combined with using tokens as a traffic engineering enforcement, a preemptive scheduling strategy in datacenters may be feasible.

We do not intend to implement the advanced system for this project, but are using it as a guideline to motivate our research. Based on the experiences and knowledge gained from implementing the basic system, we will reevaluate the feasibility and practicality of the second concept.

\subsubsection{Fault-Tolerance and Scalability}
To handle fault-tolerance we plan to integrate a fallback-mechanism to conventional TCP, if the node has not received a TCPToken in a prefixed amount of time. End-hosts will only be marginally affected by a controller or link failure, as they are guaranteed a fixed amount of bandwidth based on their token availability.
To avoid overburdening the controller, we envision a distributed hive of schedulers (e.g., Onos) each managing their own region in the final design.~\cite{onos} In case of failure, a shadow node or neighbouring device may take over computation temporarily, until the main node has recovered.~\cite{disco}

>>>>

\subsection{Overview and Goals}
In our initial simple system, "Iroko", a centralized controller regulates all 
node traffic by rate-limiting end-hosts. We have opted for a centralized 
manager in favor of a distributed protocol to leverage the advantages of a 
global network view.~\footnote{For now, we do not expect our design to scale up 
to thousands of switches. Iroko is intended for small to mid-tier size data 
centers, which may benefit from a simplistic, centralized scheduling model.}
By polling each switch individually for port and utilization statistics we are 
able to infer a global traffic matrix, which we can amalgamate with static 
routing and topology information.

Iroko guarantees minimal congestion and low average access latency. Reducing 
network-global packet loss and jitter is the priority and objective function of 
the arbiter, which will enforce these goals by restricting host bandwidth. In 
an ideal Iroko system, packet-loss will only rarely, if ever, occur. In respect 
to the free lunch theorem we aim to trade off maximum bandwidth utilization for 
optimal system stability and reliable latency.

It is important to note that routing decisions are not in the current scope of 
Iroko. While it may certainly beneficial to include dynamic and adaptive 
routing decisions in a predictive scheduler, we do not include these features 
in the current system due to time and complexity limitations. Iroko operates on 
static flow routes defined and generated by ECMP. It is assumed that these 
routes will not vary substantially and that the computed ECMP forwarding hash 
is consistent.

\subsection{Controlling traffic flow}
Rate-limiting is performed on the granularity of the IP protocol, allowing us 
to restrict traffic to specific hot regions and to package flows into groups.
End-hosts are guaranteed a limited amount of bandwidth which they may send to 
each destination address. The traffic window size for any flow is calculated 
based on the host's current traffic availability. Total bandwidth of a group of 
flows may never exceed the imposed bandwidth limitation, but nodes are free to 
distribute the allocated resources on singular subflows.

The central arbiter enforces these bandwidth and access limitations by 
assigning "tokens" to nodes. These tokens are plain information packets 
specifying the affected destination address flow, its bandwidth guarantee, and 
the expiration time. Tokens act as the rate-limiter of the system and form a 
queue each end-host will cycle through.

When a node opens a flow, it will look up the current bandwidth restriction for 
the destination IP in its token database and calculate the maximum congestion 
window possible for the particular TCP connection. In our simple design, flows 
are always assigned a fair fraction.

Once a token has expired for a particular flow-group, the restrictions of the 
next token in the queue will be applied. This mechanism is the underlying basis 
for a predictive access control algorithm and does not require any application 
level modification. On end-hosts, only the transport layer services will have 
to be modified.

\subsection{Adapting traffic flow}

Initially, the controller will compute optimal route configuration based on the 
topology and link bandwidth using a simple heuristic bin-packing approach. 
End-hosts will be initialized with a fixed low-to-medium bandwidth guarantee 
that will be adjusted over time. This bandwidth guarantee will be below the 
host's proportional bi-section bandwidth that would be used to reach any other 
host. That is, if every end host transfers using the full bandwidth initially 
allocated to it,  there would be no dropped packets due to congestion.

Of course, this would vastly underutilize network resources, thus the 
controller will dynamically adjust these allocations to ensure that hosts that 
require the bandwidth are allocated it, while host that are not currently 
utilizing all their allocated bandwidth have their allocated bandwidth reduced. 
To avoid starving hosts, some small amount of bandwidth must always be 
allocated to a given host even if it not utilizing network resources. Thus, the 
network, by design, will never reach 100\% utilization.

Conversely however one should rarely see dropped packets due to network 
congestion. Furthermore, the controller must be able to react quickly to 
changing bandwidth needs for hosts. Ideally, using a predictive method.

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Topology3}
\caption{Simple sketch of the Iroko architecture. A central scheduler maintains 
a consistent view of the current network activity and computes the optimal 
end-host bandwidth distribution. Bandwidth is enforced at end-hosts on a per-IP 
basis.}
\label{fig:Topology3}
\end{figure}

\subsection{Statistical System}
One potential implementation for our arbiter is to use reinforcement learning. 
In reinforcement learning, an agent (in our case the arbiter) performs actions 
in the environment and receives a reward signal from the environment to adjust 
its decisions in the next epoch ~\cite{Sutton:1998:IRL:551283}. The reward is 
generally used to represent the goal the agent is trying to achieve. The agent 
can freely choose whatever actions are necessary to achieve this goal 
~\cite{Sutton:1998:IRL:551283}.

The environment in this case is defined as the statistics collected from each 
switch. This decision is based on the fact that this data is easy to collect 
and provides a current snapshot of the performance of the network. We wish to 
optimize over the packet loss, and define the reward to be good if packet loss 
is decreasing (+1 reward); bad if it is increasing ( -1 reward); and acceptable 
if packet loss remains the same within a threshold (0 reward). Using this 
representation, we take full advantage of all the information provided in our 
data center; This representation is replicable and can be applied beyond the 
scope of this project.

Given the data center assumption, the number of end-hosts is known in the 
topology. We can define our arbiter's actions as a discretized representation 
among an n-dimensional vector where each cell is one of three values: increase 
decrease, or maintain the allocated bandwidth. This representation offers 
sufficient complexity. There are $3^n$ possible actions to perform and to 
achieve optimal results the agent must explore the environment extensively, 
precluding a significantly larger action space.

A potential improvement to our representation is a hierarchical learning agent. 
In this case, our arbiter would manage agents for each host and these 
sub-agents would manage their respective host whether to increase, decrease, or 
maintain bandwidth for their particular host. This problem can be referred to 
as hierarchical reinforcement learning~\cite{Borga1993}, but may prove to be 
beyond the scope of our current proposed solution, although has the added 
benefit of solving a set of sub-problems to address the global problem of 
packet loss and simplifies the representation spaces in the sub-problems.

Thus we frame our problem as one which can now be solved using techniques in 
reinforcement learning. A classic algorithm to consider is the use of 
SARSA~\cite{Sutton:1998:IRL:551283}, which is an online temporal difference 
algorithm used in classical reinforcement learning problems. One advantage of 
SARSA is its online nature~\cite{Sutton:1998:IRL:551283} which promotes more 
conservative decisions. Given full representation of our environment and 
actions, we can store information in an artificial neural network which is 
another popular choice in reinforcement learning literature. This model would 
store the reward signal information that is used to make future action choices, 
and is a theoretically proven function approximator which has made intractable 
environmental representations manageable~\cite{Sutton:1998:IRL:551283}.

%Using this model, we hope to achieve near 0% packet loss and provide a 
%%solution that gets somebody fired at google for not having tried it first.
